### 2018-07-05 paper/7-related.tex
Refer to earlier redo papers

\item \Redo~\cite{redo} almost exactly matches \Shake at the level of detail
given here, differing only on aspects like polymorphic
dependencies~\S\ref{sec-polymorphism}.

>>>>

\item \Redo~\cite{redo-idea}\cite{grosskurth2007redo}\cite{redo} almost exactly
matches \Shake at the level of detail given here, differing only on aspects like
polymorphic dependencies~\S\ref{sec-polymorphism}.
